`conmat`: generate synthetic contact matrices for a given age-stratified population

### 2025-03-04 paper/paper.qmd
don't use cite-method: biblatex

---
title: '`conmat`: generate synthetic contact matrices for a given age-stratified population'
authors:
- affiliation: 1
  name: Nicholas Tierney
  orcid: 0000-0003-1460-8722
- affiliation: 1,3
  name: Chitra Saraswati
  orcid: 0000-0002-8159-0414
- affiliation: 1,3
  name: Aarathy Babu
  orcid: 
- affiliation: 4
  name: Michael Lydeamore
  orcid: 0000-0001-6515-827X
- affiliation: 1,2
  name: Nick Golding
  orcid: 0000-0001-8916-5570
date: today
bibliography: paper.bib
cite-method: biblatex
tags:
- epidemiology
- R
- infectious disease
affiliations:
- index: 1
  name: The Kids Research Institute Australia, WA, Australia
- index: 2
  name:  University of Western Australia, WA, Australia
- index: 3
  name: Monash University, VIC, Australia
execute: 
  echo: true
  cache: false
format: 
  html: 
    keep-md: true
    fig-height: 4
    fig-align: center
    fig-format: png
    dpi: 300
---

>>>>

---
title: '`conmat`: generate synthetic contact matrices for a given age-stratified population'
authors:
- affiliation: 1
  name: Nicholas Tierney
  orcid: 0000-0003-1460-8722
- affiliation: 1,3
  name: Chitra Saraswati
  orcid: 0000-0002-8159-0414
- affiliation: 1,3
  name: Aarathy Babu
  orcid: 
- affiliation: 4
  name: Michael Lydeamore
  orcid: 0000-0001-6515-827X
- affiliation: 1,2
  name: Nick Golding
  orcid: 0000-0001-8916-5570
date: today
bibliography: paper.bib
tags:
- epidemiology
- R
- infectious disease
affiliations:
- index: 1
  name: The Kids Research Institute Australia, WA, Australia
- index: 2
  name:  University of Western Australia, WA, Australia
- index: 3
  name: Monash University, VIC, Australia
execute: 
  echo: true
  cache: false
format: 
  html: 
    keep-md: true
    fig-height: 4
    fig-align: center
    fig-format: png
    dpi: 300
---
